---
title: "Regression Results"
format: html
editor: visual
author: "Lennart Joop and Julia Daetz"
bibliography: references.bib
echo: false
warning: false
---

The following document presents the regression results of our work in accordance to milestone 4 "Results".

### OLS Regression without control variables

## Regression tables

```{r,include=FALSE}
library(here)
library(fixest)
source(here("output1","Master_Script.R"))
source(here("output1","Regression.R"))
```

```{r}
etable(feols(data=simple.lm.per1,DiffTotal2017~Election2017), feols(data=simple.lm.per2,DiffTotal2018~Election2017),digits="r3", fitstat=c('n','ar2'), headers=c("case 1","case 2"))

etable(
       feols(data=simple.lm.per3,DiffTotal2021~Election2021),
       feols(data=simple.lm.per4,DiffTotal2022~Election2021),
digits="r3", fitstat=c('n','ar2'), headers=c( "case 3", "case 4" ))
```

## Result description

All our result are positive, ranging in between 0.34 and 1. In both election years the estimator is higher after the 15 month period in comparison to the 3 month period. For case 1 the result is not significant, for case 2,3 and 4, the results are in the 95% confidence interval. The explanation power of the model (R2) is higher for the 2021 election then the 2017 election and in both years higher for the 15 months period then the 3 months period. With case 4 having the highest R2 of 0,37, the overall explanation power of the model is still low. Voting results of the AfD alone are not enough to explain the change of EU migrants.

### OLS Regression with control variables

## Regression tables

```{r}
etable(feols(data=simple.lm.per1,DiffTotal2017~Election2017+Big.City+East.Germany+Total2016+Unemployment2017+PurchasePower2017+KH2017), feols(data=simple.lm.per2,DiffTotal2018~Election2017+Big.City+East.Germany+Total2016+Unemployment2018+PurchasePower2018+KH2018), 
digits="r3", fitstat=c('n','ar2'), headers=c("case 1","case 2"))

etable(feols(data=simple.lm.per3,DiffTotal2021~Election2021+Big.City+East.Germany+Total2020+Unemployment2021+PurchasePower2021+KH2021),
feols(data=simple.lm.per4,DiffTotal2022~Election2021+Big.City+East.Germany+Total2020+Unemployment2021+PurchasePower2021+KH2021),
digits="r3", fitstat=c('n','ar2'), headers=c("case 3","case 4") )
```

## Result description

After including control variables, our regression results are still positive, varying between 0.03 for case 3 and 0.752 for case 2. The introduction of control variables also increases our explanatory power significantly, especially in the 2017 election. The R2 increases to 0,74 and 0,66 for case 1 and 2, and only slightly increases for case 3 and 4 to 0.46 and 0.50 respectively. Similar to the regression without control variables, the estimator increases in the 15 month period compared to the 3 month period. The result is not significant for case 3, but significant for case 1, 2 and 4.

From the control variables we used, the baseline amount of migrants (Total2016 and Total2020) and the purchasing power (PurchasePower2017, PurchasePower2018 and PurchasePower2021) have close to no impact at all. The unemployment rate (Unemployment2017, Unemployment2018 and Unemployment2021) has a negative impact for case 2, 3 and 4 but a positive one for case 1. The helathcare control variable (KH2017, KH2018 and KH2021) has a positive impact for the 2017 election and a negative impact for the 2021 election. The Big City control variable has a huge positive influence in the 2017 election. The difference between being in one of the big cities or not has an impact on the percentage migrant increase of 87 points for case 1 and 41 points for case 2. For the 2021 election the impact is significantly smaller and negative: -0,2 for case 3 and -1.3 for case 4. This difference between the two election years is huge. The East Germany control variable has a pretty large negative impact for case 1 and 2 of -15,3 and -5.5, but on the contrary a pretty large positive impact for case 3 and 4 of 3.7 and 6.8

## Conclusion

The findings from [OLS Regression without control variables] are straightforward and confirm the graphical data visualization. There is a positive relation between AfD voting results and the percentage increase of migrants in voting districts.

Because of the xenophobic nature of the AfD we assumed that this positive relation is driven by other variables and that this finding does not reflect the real nature of the correlation, which we expected to be negative. By including control variables that catch other destination-deciding effects, like income, access to healthcare and the attractiveness of big cities, we tried to isolate the effect.

However, the results of the regression did not confirm our initial intuition. The inclusion of control variables did not change the direction of the relationship or the magnitude, the estimators vary slightly, but are still in the same range. Additionally, the estimators of some of the control variables were different from our estimations. We would have assumed a strong positive impact of big cities on migration decisions. This holds true for the year 2017 but is completely reversed for the year 2021. Also purchasing power having close to zero impact is very surprising to us, as incomes of regions should be a strong incentive for EU migrants to move.

On the other hand, the positive estimator for unemployment in case 1 and the negative estimators for cases 2, 3, and 4 are logical. Higher unemployment may indicate more job opportunities for migrants, while lower unemployment could be associated with wealthier regions that are more attractive to migrants. Therefore, it makes sense to have mixed estimators.

Our last control variable, the number of hospital beds per 1000 inhabitants, being an indicator for access to healthcare in one region, also shows mixed estimators. This does not follow our intuition, since we expected access to healthcare and therefore better quality of living to have pulling effects on migrants.

These findings pose the question, why our initial theory - the relationship between AfD election results, our control variables and EU migrant movements inside Germany - differs from our regression results. There are multiple possible explanations:

**Explanation A):**

Our initial theory was correct and there indeed exists a negative relationship, which we failed to capture due to limitations of our model. These limitations could be the following:

1.  Weighting federal districts by area to assign population does not reflect the real distribution of population. As a consequence the migrant data we assigned to voting districts is false. To solve this, further research should look even deeper into the German organisational structure and actually assign the data of each village or small city to the corresponding federal district to get more accurate data.

2.  Our control variables do not catch the real drivers of migration movements. We tried to control for economic factors, social factors and quality of living factors inside Germany. While our model quality improved after controlling, the impact of some of the variables is either close to 0 (total amount of migrants, purchasing power) or different then we would have expected (big cities).

    Alternatively to missing socioeconomic factors in Germany, not controlling for factors *outside* of Germany (conditions in home countries of migrants) due to matters of practicality, might have falsified the results of our study.

**Explanation B):**

The results, suggesting a positive relationship between the two variables, actually do reflect the reality, in which case our initial intuition was wrong. There might be a high number of EU migrants agreeing with the political stance of the AfD. Although the party is xenophobic, this stance might be more directed towards non-EU countries such as the northern African countries, who were the main drivers of the migration crisis in 2015. Other EU foreigners might actually favor such a stance leading to the positive estimators.

**Explanation C):**

AfD election results do not impact migration decisions of EU foreigners in Germany, in which case our model mistakenly showed a positive relationship. Although the model shows a significant positive estimator, this estimator is small compared to the most impactful control variables big cities and east/west Germany. EU migrants might just not care about politics inside Germany and especially about the voting results of one particular party. Voting districts, that favor the AfD, might not feel more xenophobic for EU migrants. Considering, that the AfD was seen as less radical in the past, the voting results of the party might not influence migrants to such a big degree.
