---
title: "Regression Results"
format: html
editor: visual
author: "Lennart Joop and Julia Daetz"
bibliography: references.bib
echo: false
warning: false
---

The following document presents the regression results of our work in accordance to milestone 4 "Results".

### OLS Regression without control variables

## Regression tables

```{r,include=FALSE}
library(here)
library(fixest)
source(here("output1","Master_Script.R"))
source(here("output1","Regression.R"))
```

```{r}
etable(feols(data=simple.lm.per1,DiffTotal2017~Election2017), feols(data=simple.lm.per2,DiffTotal2018~Election2017),digits="r3", fitstat=c('n','ar2'), headers=c("case 1","case 2"))

etable(
       feols(data=simple.lm.per3,DiffTotal2021~Election2021),
       feols(data=simple.lm.per4,DiffTotal2022~Election2021),
digits="r3", fitstat=c('n','ar2'), headers=c( "case 3", "case 4" ))
```

## Result description

All our result are positive, ranging in between 0.34 and 1. In both election years the estimator is higher after the 15 month period in comparison to the 3 month period. For case 1 the result is not significant, for case 2,3 and 4, the results are in the 95% confidence interval. The explanation power of the model (R2) is higher for the 2021 election then the 2017 election and in both years higher for the 15 months period then the 3 months period. With case 4 having the highest R2 of 0,37, the overall explanation power of the model is still low. Voting results of the AFD alone are not enough to explain the change of EU migrants.

From the control variables we used, the baseline amount of migrants (Total2016 and Total2020) and the purchasing power (PurchasePower2017, PurchasePower2018 and PurchasePower2021) have close to no impact at all. 
### OLS Regression with control variables

## Regression tables

```{r}
etable(feols(data=simple.lm.per1,DiffTotal2017~Election2017+Big.City+East.Germany+Total2016+Unemployment2017+PurchasePower2017+KH2017), feols(data=simple.lm.per2,DiffTotal2018~Election2017+Big.City+East.Germany+Total2016+Unemployment2018+PurchasePower2018+KH2018), 
digits="r3", fitstat=c('n','ar2'), headers=c("case 1","case 2"))

etable(feols(data=simple.lm.per3,DiffTotal2021~Election2021+Big.City+East.Germany+Total2020+Unemployment2021+PurchasePower2021+KH2021),
feols(data=simple.lm.per4,DiffTotal2022~Election2021+Big.City+East.Germany+Total2020+Unemployment2021+PurchasePower2021+KH2021),
digits="r3", fitstat=c('n','ar2'), headers=c("case 3","case 4") )
```

## Result description

After including control variables, our regression results are still positive, varying between 0.03 for case 3 and 0.752 for case 2. The  The introduction of control variables also increases our explanation power significantly, especially in the 2017 election. The R2 increases to 0,74 and 0,66 for case 1 and 2, and only slightly increases for case 3 and 4 to 0.46 and 0.50 respectively. Similar to the regression without control variables, the estimator increases in the 15 month period compared to the 3 month period. Again the result is not significant for case 1, but significant for case 2,3 and 4. 


## Conclusion and Discussion



