---
title: "Robustness"
format: html
editor: visual
author: "Lennart Joop and Julia Daetz"
bibliography: references.bib
warnings: false
echo: false
---

This document is used to present the robustness of our results, according to milestone 5.

## Control Variables

By including control variables into our main regression we already improved the precision of our model and managed to improve our R2 values from 0.01 and 0.14 in case 1 and 2 to 0.74 and 0.66, and from 0.27 and 0.37 in case 3 and 4 to 0.46 and 0.50. Especially in 2017 the introduction of the control variables improved the model greatly, while in 2021 the improvement was less significant. For further information on that topic see [Dataset](./Dataset.html) and [Regression Results](./Regression_Results.html).

## Reverse Causality

One of our main concerns is the possibility of reverse causality. What if AfD vote shares do not influence migration numbers, but instead, migration numbers influence AfD vote shares? To test this hypothesis we conducted a reverse regression, where we used the migration numbers as the dependent variable and the AfD numbers as the independent variable. We did this regression both with and without control variables.

```{r,include=FALSE}
library(here)
library(fixest)
source(here("output1","Master_Script.R"))
source(here("output1","Regression.R"))
```

```{r}
etable(feols(data=simple.lm.per1,Election2017~DiffTotal2017), feols(data=simple.lm.per3,Election2021~DiffTotal2021),digits="r3", fitstat=c('n','ar2'), headers=c("2017","2021"))

etable(feols(data=simple.lm.per1,Election2017~DiffTotal2017+Big.City+East.Germany+Total2016+Unemployment2017+PurchasePower2017+KH2017),
  feols(data=simple.lm.per3, Election2021~DiffTotal2021+Big.City+East.Germany+Total2020+Unemployment2021+PurchasePower2021+KH2021),digits="r3", fitstat=c('n','ar2'), headers=c( "2017", "2021" ))
```

The influence of percentage migration numbers is significant in both years but in 3 of 4 cases very close to zero. This indicates that we indeed have a causal relationship from AfD numbers to migration numbers and not the other way around. The inclusion of control variables does not change this result.
